Implications of afforestation policies for global markets

### 2024-02-27 paper.Rmd
Update paper.Rmd

Table 5. Change in consumer well-being in 2033, by region, in dollars, with deforestation mitigation policy in place (Source: GTAP EV) 
				$\Delta$ ($)
Japan				977,125,000
Canada				166,937,500
Oceania				-169,625,000
Brazil				-735,125,000
Rest of South America		-3,848,625,000
United States			-1,085,000,000
Russia				-1,152,375,000
Central America			-4,471,500,000
North Africa & the Middle East	-5,012,125,000
East Asia			-5,065,625,000
West & Central Europe		-7,152,500,000
Sub-Saharan Africa		-7,850,500,000
Southeast Asia			-13,601,000,000
China				-14,452,000,000
South Asia			-28,024,000,000

@@

@@

<!-- [@defries2010] found a strong correlation between forest loss and exports of agricultural products. On the other hand, [@turner2005] investigated the role of trade on forests in the context of the Free Trade Area of the Americas (FTAA) using the spatial partial-equilibrium Global Forest Products Model and found that FTAA has a positive impact on forest resources. -->
# References

>>>>

out = rbind(out, `$\\Delta$ ($)` = worldGTAP$EV-baselineGTAP$EV)
)
rownames(out) = regLabels[gGTM[rownames(out)]]

kableExtra::column_spec(
  kableExtra::column_spec(kableExtra::kable_styling(
    knitr::kable(out, caption = 'Change in consumer well-being in 2033, by region, in dollars, with deforestation mitigation policy in place', digits = 1, escape = FALSE, label = 'baseline-scenario1')
  ), 1, border_left = TRUE),
  5,
  border_right = TRUE
)

```
Table 5. Change in consumer well-being in 2033, by region, in dollars, with deforestation mitigation policy in place (Source: GTAP EV) 
				$\Delta$ ($)
Japan				977,125,000
Canada				166,937,500
Oceania				-169,625,000
Brazil				-735,125,000
Rest of South America		-3,848,625,000
United States			-1,085,000,000
Russia				-1,152,375,000
Central America			-4,471,500,000
North Africa & the Middle East	-5,012,125,000
East Asia			-5,065,625,000
West & Central Europe		-7,152,500,000
Sub-Saharan Africa		-7,850,500,000
Southeast Asia			-13,601,000,000
China				-14,452,000,000
South Asia			-28,024,000,000

@@

# References

@@

<!-- [@defries2010] found a strong correlation between forest loss and exports of agricultural products. On the other hand, [@turner2005] investigated the role of trade on forests in the context of the Free Trade Area of the Americas (FTAA) using the spatial partial-equilibrium Global Forest Products Model and found that FTAA has a positive impact on forest resources. -->
